Non-word repetition in Yélî Dnye

### 2020-09-14 manuscript.Rmd
minor footnote updates

[^1]: Precise years of education can be hard to count. This is particularly the case for schooling beyond grade 8, which takes place off-island, due to an irregularity in ability to pay school fees, school opening times, familial obligations, and more. We asked parents to report their highest completed level of education and inferred the approximate number of years that entails under ideal conditions, which results in many esimates around typical "completion" times.

>>>>

[^1]: Precise years of education can be hard to count. This is particularly the case for schooling beyond grade 8, which takes place off-island, which can be due to an irregularity in ability to pay school fees, school opening times, familial obligations, and more. We asked parents to report their highest completed level of education and inferred the approximate number of years that entails under ideal conditions, which results in many esimates around typical "completion" times in between.
